---
title: "lab 7"
author: "Claire Meuter"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#attach packaages 
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro to ggpairs

Use GGally::ggpairs() function to create a pair plot
```{r}
ggpairs(penguins)
```

```{r}
penguins %>%
  select(species, bill_length_mm:body_mass_g) %>% # the : keeps bill length through body mass
  ggpairs(aes(color = species))#we can customize further like colors by species


#I might seperatly want to look a penguins bill depth and body mass

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group_by = species)) + geom_point(aes(color = species)) + geom_smooth(method = "lm")
```
body mass seems to be lineraly related 
lm-linear model

## Multiple linear regression - penguins 
use multiple linear regression to try to understand the relationship between multiple predictor variables and a signle continous outcome variable (body mass)

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

#return just the coefficients by running name
penguin_lm
```
How would you intreperate this co-efficient for flippper length? 
On average we would expect a 1 mm increase in flipper length to be assciated with a 51.54 g increase in body mass if everything else is consant. 
We would expect a 22.63 g increase in body mass for each 1mm increase in bill depth 

We can use the summary function to get more information 
```{r}
summary(penguin_lm)
```

For bill depth we CANNOT reject the null hypothesis- can still impact other variables, but the P-value is not significant 
75% of varaiance in our penguin mass is explained in this model 


## Usse 'broom' functions tiday and glance 
use broom;;tidy to get the coefficient summary in a data frame
use broom::glance to the model summary in a data frame 

```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy 
```

Use in line code to find bill depth estimate
`r penguin_lm_tidy$estimate[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```


## Try another model 
We have thought really hard, done a lit review, consulted experts, explored data, and decided most important variables to include are:
- flipper length
- species
- sex

Task: create a multiple linear regression model using those 3 predictor variables 
```{r}
penguinlm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguinlm_2
```

Adele penguins are reference, female is reference
mass(g) = -365.82 + 20.02(flipper length mm) - 87.63(chinstrap) + 836.26(gentoo) + 530.38(male)

Use augment to see predicted values vs actual values
```{r}
augment(penguinlm_2)
```

## use plot to look at model dignostics 
```{r}
plot(penguinlm_2)
```


- concpetual ucerstanding and expertise allows me to resposibly determine that penguin species, sex, and flipper length are reasonable predictor variable (make sure you're thinking hard about variables and different variable combinations)
-Diagnostic plots all check out for normality of residuals, homocedasticity, and no worrisome outliers(<<last on eis not an assumption)

## Make output tables 

Using model summary: 
```{r}
modelsummary(penguinlm_2)
```

Using stargazer

```{r, results = "asis"}
stargazer(penguinlm_2, type = "html")
```

